\label{ch:diceware}

\Character[margaret - a hacker]{Margaret}{marge}
\Character[harriet - a friend]{Harriet}{harriet}

\scene

\begin{drama}
\StageDir{Two women sit in a dark room in front of a computer.}
\margespeaks This information needs to stay secret.
\harrietspeaks Calm down, it's encrypted with a password nobody can guess: r 4 b @ b 1 t \$
\margespeaks A simple word with substitutions and insertions? You've got to be kidding me, Harriet, a twelve-year-old computer could break that in milliseconds. 
\harrietspeaks Then you make the password.
\margespeaks \direct{grabs four dice} I'll make a Diceware passphrase.
\StageDir{\marge rolls the dice}
\margespeaks 1 6 6 6; that's \textit{cognitive}.
\StageDir{She rolls the dice again}
\margespeaks 5 1 5 6; that's \textit{poetic}.
\harrietspeaks What's a passphrase?
\margespeaks A password made from words stuck together. And with enough words chosen randomly, reasonably secure.
\StageDir{\marge rolls the dice three more times}
\harrietspeaks How obscure; I'll never remember these numbers.
\margespeaks 5 3 5 6 3 2 2 3 5 6 2 6; your passphrase is \textit{cognitive poetic ribbon garlic smelliness}.
\harrietspeaks I won't call that poetic, but I can probably remember it. Thanks, Marge.
\end{drama}

\setlength{\parindent}{0em}
\setlength{\parskip}{.75em}

\subsubsection*{What is a Diceware passphrase?}

A passphrase is a list of words that you type into your computer to let it know for sure that \textit{the person typing is you}. Passphrases differ from passwords only in length.

Diceware is a method for picking passphrases which uses dice to select words at random from a special list. Each word in the list is preceded by a four digit number. All the digits are between one and six, allowing you to use the outcomes of four dice rolls to select a word from the list.

\subsubsection*{Directions}

\begin{itemize}[leftmargin=*]

\setlength\itemsep{.75em}

\item[1] Decide how many words you want in your passphrase. A five-word passphrase provides a level of security \textit{much} higher than the passwords most people use. For NSA-proof security, use seven words.

\item[2] Roll all four dice at once and write the results down, reading from left to right, on a scrap of paper. Make as many of these four-digit groups as you want words in your passphrase.

\item[3] Flip to the word list and look up the corresponding word next to each four-digit number.

\item[4] The words you have found are your new passphrase!

\item[5] Come up with a way to remember your phrase. It might be a story, mental picture, or sentence that will remind you of the phrase you generated.

\end{itemize}

Your passphrase is one of the 3,656,158,440,062,976 ($6^{20}$) alternatives that could have been chosen by this method.

%\setlength{\parskip}{0.5em}
%
%\subsubsection*{Example}
%
%Suppose you want a five-word passphrase. You will need $5 \times 4$ or 20 dice rolls. Let's say they come out as:
%
%\begin{adjustwidth}{2em}{2em}
%	\makebox[\linewidth][s]{\textit{1 6 6 6 5 1 5 6 5 3 5 6 3 2 2 3 5 6 2 6}}
%\end{adjustwidth}
%
%Write the results on a scrap of paper in groups of four:
%
%\begin{adjustwidth}{2em}{2em}
%	\textit{1 6 6 6 \\
%		5 1 5 6 \\
%		5 3 5 6 \\
%		3 2 2 3 \\
%		5 6 2 6}
%\end{adjustwidth}
%
%You then look up each group of five rolls in the Diceware word list by finding the number in the list and writing down the word next to the number:
%
%\begin{adjustwidth}{2em}{2em}
%	\textit{1666 cognitive \\
%		5156 poetic \\
%		5356 ribbon \\
%		3223 garlic \\
%		5626 smelliness}
%\end{adjustwidth}
%
%Your passphrase would then be:
%
%\begin{adjustwidth}{2em}{2em}
%	\textit{cognitive poetic ribbon garlic smelliness}
%\end{adjustwidth}
%
%This passphrase is one of the 3,656,158,440,062,976 ($6^{20}$) alternatives that could have been chosen by this method.
%
%%(\approx$2^{51}$) 
%
%\setlength{\parskip}{0.25em}
